Supplementary Materials

### 2019-01-30 sup_mat/sup_mat.Rmd
added some details to AC

## Adaptive Choice
For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance. The search display consisted of 54 small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?). the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive. On every trial, just one blue and one red square contained a number between 2 and 5. Participants were instructed to find and report one of them. To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside. The distractor blue and red squares would always contain numbers between 6 and 9. The green squares contained numbers between 2 and 9. Participants were instructed to complete the task as quickly and as accurately as possible.

@@

## Split-Half
Accuracy data is shown in Figure \ref{fig:acc_plt}. From this we can see that there are a number of outliers: 15, 25, 47, and 48. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

@@

>>>>

## Adaptive Choice
For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance. The search display consisted of two target squares (one red and one blue), and 52 distractor squares: 12 red, 12 blue, 14 green, and 14 squares of variable colour, arranged in three rings around a fixation point. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive. On every trial, just one blue and one red square contained a number between 2 and 5. Participants were instructed to find and report one of them. To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside. The distractor blue and red squares would always contain numbers between 6 and 9. The green squares contained numbers between 2 and 9. Participants were instructed to complete the task as quickly and as accurately as possible.

@@

## Participant exclusions in the Split-Half task
Accuracy data is shown in Figure \ref{fig:acc_plt}. From this we can see that there are a number of participants who did not perform the task to a reasonable standard: 15, 25, 47, and 48. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials. This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.

@@

The
